Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-01-09 paper/appendix.tex
Prepare thesis for PCSC

%\section{Introduction to the Appendices}

%The Appendices is where you are enabled to present any additional or supplementary information relevant to your study, yet do not require highlighting within the actual paper, either because of its trivial nature or volume. These may in the form of figures, tables, or additional text detailing specific aspects about or related to the study.

%\section{Sample Questions for Different Studies}
%The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper. You may use this as another reference in writing your paper.
\chapter{CORRECTION FOR DASGUPTA--PAL}
\label{chap:correction}
\section{Bitwise Description of the Dasgupta--Pal Cryptosystem}
The Dasgupta--Pal cryptosystem \cite{dasgupta_design_2016} encrypts each bit in a bit string independently.
In terms of the encryption of a single bit, the Dasgupta--Pal cryptosystem can be described as follows:
\begin{description}
	\item[Key generation]
	Let the secret key, $S_k$ be a large prime.
	Let the public refresh key, $R_k$, be $S_k \times z$, where $z$ is a large even integer.
	\item[Encryption]
	Given a message $m$, the encryption function is defined as
	\begin{align*}
		E(m) = m + S_kr
	\end{align*}
	where $r$ is a random integer.
	\item[Decryption]
	Given a ciphertext $c$, the decryption function is defined as
	\begin{align*}
		D(c) = c \bmod S_k \bmod 2
	\end{align*}
\end{description}
The homomorphic operations are then defined as
\begin{description}
	\item[XOR on ciphertexts]
	\begin{align*}
		D(E(a)+E(b)) = a \text{ XOR } b = (a + b) \bmod 2
	\end{align*}
	\item[AND on ciphertexts]
	\begin{align*}
		D(E(a)\times E(b)) = a \text{ AND } b = ab \bmod 2
	\end{align*}
\end{description}
After repeated operations on ciphertexts, the resulting ciphertext can grow in magnitude.
To prevent storage issues and keep the ciphertext size small, a refresh function is used.
\begin{description}
	\item[Refresh function]
	Given a ciphertext $c$, the refresh function is defined as
	\begin{align*}
		R(c) = c \bmod R_k
	\end{align*}
\end{description}
\section{Cases Where Decryption Fails}
We consider the following quantity:
\begin{align}
	\label{eq:cornercase_ciphertext}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}}).
\end{align}
Since $S_k$ is odd, the corresponding operation in the plaintext space is
\begin{align*}
	\label{eq:cornercase_plaintext}
	\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1.
\end{align*}
However, evaluating Equation \ref{eq:cornercase_ciphertext} yields:
\begin{align*}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})
	&= D\left(\sum_{i=1}^{S_k}{(1+S_kr_i)}\right)\\
	&= D\left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right)\\
	&= \left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right) \bmod S_k \bmod 2\\
	&= 0 \bmod 2\\
	&= 0.
\end{align*}
Since $\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1\neq 0 = D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.

\section{Proposed Correction and Proof of Correctness}
We now show that setting the secret key $S_k$ to $2p$, where $p$ is a prime, fixes the issue in the original cryptosystem.
\begin{theorem}
	Suppose $S_k = 2p$, where $p$ is a prime. Then when addition or multiplication is performed between any two ciphertexts, correct decryption is assured.
\end{theorem}
\begin{proof}
	Suppose $c_1, c_2$ are two ciphertexts such that
	\begin{align*}
		c_1 = a + S_kr_1\\
		c_2 = b + S_kr_2
	\end{align*}
	We first consider addition. We want to show that $(c_1+c_2)\bmod S_k$ has the same parity as $a+b$.
	By the division algorithm, we have $a+b = S_kq + r$, for some $q,r$, $q \geq 0, r > 0$. We can rewrite $c_1+c_2$ as
	\begin{align*}
		c_1+c_2 &= (a + S_kr_1) + (b + S_kr_2)\\
		&= (a+b)+ S_k(r_1 + r_2)\\
		&= (S_kq + r) + S_k(r_1 + r_2)\\
		&= r + S_k(q + r_1 + r_2).
	\end{align*}
	Therefore $(c_1+c_2)\bmod S_k = r$.
	It is enough to show that the parity of $a+b$ is the same as the parity of $r$. We consider cases based on the parity of $a+b$.
	\begin{description}
		\item[Case 1: $a+b$ is odd.]
			Since $a+b = S_kq + r$, $S_kq + r$ must also be odd.
			$S_k$ is even, so $S_kq$ is also even.
			For $S_kq + r$ to be odd, $r$ must be odd, since $S_k$ is even.

@@

>>>>

\section{Correction for Dasgupta--Pal}
\label{chap:correction}
\subsection{Bitwise Description of the Dasgupta--Pal Cryptosystem}
The Dasgupta--Pal cryptosystem \cite{dasgupta_design_2016} encrypts each bit in a bit string independently.
In terms of the encryption of a single bit, the Dasgupta--Pal cryptosystem can be described as follows:
\begin{description}
	\item[Key generation]
	Let the secret key, $S_k$ be a large prime.
	Let the public refresh key, $R_k$, be $S_k \times z$, where $z$ is a large even integer.
	\item[Encryption]
	Given a message $m$, the encryption function is defined as
	\begin{align*}
		E(m) = m + S_kr
	\end{align*}
	where $r$ is a random integer.
	\item[Decryption]
	Given a ciphertext $c$, the decryption function is defined as
	\begin{align*}
		D(c) = c \bmod S_k \bmod 2
	\end{align*}
\end{description}
The homomorphic operations are then defined as
\begin{description}
	\item[XOR on ciphertexts]
	\begin{align*}
		D(E(a)+E(b)) = a \textsc{ xor } b = (a + b) \bmod 2
	\end{align*}
	\item[AND on ciphertexts]
	\begin{align*}
		D(E(a)\times E(b)) = a \textsc{ and } b = ab \bmod 2
	\end{align*}
\end{description}
After repeated operations on ciphertexts, the resulting ciphertext can grow in magnitude.
To prevent storage issues and keep the ciphertext size small, a refresh function is used.
\begin{description}
	\item[Refresh function]
	Given a ciphertext $c$, the refresh function is defined as
	\begin{align*}
		R(c) = c \bmod R_k
	\end{align*}
\end{description}
\subsection{Cases Where Decryption Fails}
We consider the following quantity:
\begin{align}
	\label{eq:cornercase_ciphertext}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}}).
\end{align}
Since $S_k$ is odd, the corresponding operation in the plaintext space is
\begin{align*}
	\label{eq:cornercase_plaintext}
	\underbrace{1 \textsc{ xor } 1 \textsc{ xor } \cdots \textsc{ xor } 1}_{S_k \text{ times}} = 1.
\end{align*}
However, evaluating Equation \ref{eq:cornercase_ciphertext} yields:
\begin{align*}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})
	&= D\left(\sum_{i=1}^{S_k}{(1+S_kr_i)}\right)\\
	&= D\left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right)\\
	&= \left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right) \bmod S_k \bmod 2\\
	&= 0 \bmod 2\\
	&= 0.
\end{align*}
Since $\underbrace{1 \textsc{ xor } 1 \textsc{ xor } \cdots \textsc{ xor } 1}_{S_k \text{ times}} = 1\neq 0 = D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.

\subsection{Proposed Correction and Proof of Correctness}
We now show that setting the secret key $S_k$ to $2p$, where $p$ is a prime, fixes the issue in the original cryptosystem.
\begin{theorem}
	Suppose $S_k = 2p$, where $p$ is a prime. Then when addition or multiplication is performed between any two ciphertexts, correct decryption is assured.
\end{theorem}
\begin{proof}
	Suppose $c_1, c_2$ are two ciphertexts such that
	\begin{align*}
		c_1 = a + S_kr_1\\
		c_2 = b + S_kr_2
	\end{align*}
	We first consider addition. We want to show that $(c_1+c_2)\bmod S_k$ has the same parity as $a+b$.
	By the division algorithm, we have $a+b = S_kq + r$, for some $q,r$, $q \geq 0, r > 0$. We can rewrite $c_1+c_2$ as
	\begin{align*}
		c_1+c_2 &= (a + S_kr_1) + (b + S_kr_2)\\
		&= (a+b)+ S_k(r_1 + r_2)\\
		&= (S_kq + r) + S_k(r_1 + r_2)\\
		&= r + S_k(q + r_1 + r_2).
	\end{align*}
	Therefore $(c_1+c_2)\bmod S_k = r$.
	It is enough to show that the parity of $a+b$ is the same as the parity of $r$. We consider cases based on the parity of $a+b$.
	\begin{description}
		\item[Case 1: $a+b$ is odd.]
			Since $a+b = S_kq + r$, $S_kq + r$ must also be odd.
			$S_k$ is even, so $S_kq$ is also even.
			For $S_kq + r$ to be odd, $r$ must be odd, since $S_k$ is even.

@@

\section{Numerical Approximations}
\newcommand*\diff{\mathop{}\!\mathrm{d}}

Transcendental functions such as the exponential and logarithmic functions are usually implemented in computer hardware and software libraries using minimax polynomials, which are determined numerically using the Remez algorithm \cite{harrison_computation_1999}.
However, the Remez algorithm relies on iteratively refining the polynomial coefficients, which requires knowledge of the argument passed to the exponential or logarithmic function.

We cannot directly apply this approach in privacy-preserving image processing as we do not have knowledge of the exact value of the function arguments. In order to calculate a function under a  homomorphic cryptosystem, it is necessary to express the function in terms of the homomorphic operations.
In this section, we discuss approximations for the logarithm ($\log(1+x)$) and power ($x^r$) functions using only addition, subtraction, multiplication, and division operations.

%TODO: Explain why standard methods for transcedental function approximation cannot be applied here.
%TODO: Include citations for this chapter
\subsection{Approximation for $\log(1+x)$}
\label{sec:logapproximation}
We approximate the function $f(x)=\log(1+x)$ using a similar method to that described in
\cite{khattri_new_2009}.
We let $x = 1/n$ and consider the integral
\begin{align*}
  \int_{n}^{n+1}{\frac{1}{x}\diff x}=\log{\left(1+\frac{1}{n}\right)}.
\end{align*}

This integral can be approximated using the five-point Gauss-Legendre quadrature rule \cite{kythe_quadrature_2002}, which is as follows:
\begin{align*}
	\int_a^b{f(x)\diff x}
	&= \frac{b-a}{2}\int_{-1}^{1}{f\left(\frac{b-a}{2}x+\frac{a+b}{2}\right)\diff x}\\
	\int_{-1}^{1}{f(x)\diff x} &= \sum_{i=1}^{5}{w_if(x_i)}
\end{align*}
where
\begin{multicols}{2}
	\noindent
	\begin{align*}
		w_1 &= 0\\
		w_2 &= \frac{1}{21}\sqrt{245-14\sqrt{70}}\\
		w_3 &= -\frac{1}{21}\sqrt{245-14\sqrt{70}}\\
		w_4 &= \frac{1}{21}\sqrt{245+14\sqrt{70}}\\
		w_5 &= -\frac{1}{21}\sqrt{245+14\sqrt{70}}\\
	\end{align*}
	\columnbreak
	\begin{align*}
		x_1 &= \frac{128}{225}\\
		x_2 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
		x_3 &= \frac{1}{900}\left( 322 + 13\sqrt{70}\right)\\
		x_4 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
		x_5 &= \frac{1}{900}\left( 322 - 13\sqrt{70}\right)\\
	\end{align*}
\end{multicols}
This yields the following approximation:
\begin{equation}\label{eq:standardquadrature}
  \log(1+x) \approx
  \frac{137x^5 + 2310x^4 + 9870x^3 + 15120x^2 + 7560x}
  {30x^5 + 900x^4 + 6300x^3 + 16800x^2 + 18900x + 7560}.
\end{equation}
While this closed form approximation is accurate for values of $x$ near zero, it diverges from $\log{(1+x)}$ significantly for large values of $x$.
\begin{figure}[!ht]
    \centering
    \includegraphics[width=.8\linewidth]{figures/StandardQuadrature.png}
    \caption{Graph of $\log{(1+x)}$ and the approximation in equation \ref{eq:standardquadrature}}
    \label{fig:standardquadrature}
\end{figure}
As we only need accuracy for $x \in [0, 255]$, we can scale the approximation by a constant factor $\alpha$ as follows:
\begin{align*}
  \log{(1+x)} &= \log{\left(\frac{\alpha + \alpha x}{\alpha}\right)}\\
  &= \log{(\alpha + \alpha x)} - \log{\alpha}\\
  &= \log{\left(\alpha+\frac{\alpha}{n}\right)} - \log{\alpha}\\
  &= \log{\left(\frac{\alpha n + \alpha}{n}\right)} - \log{\alpha}\\
  &= \int_{n}^{\alpha n + \alpha}{\frac{1}{x}\diff x} - \log{\alpha}
\end{align*}

Using the five-point Gauss-Legendre quadrature rule with $\alpha = 1/20$, we arrive at the approximation:
\begin{align}\label{eq:scaledquadrature}
  \begin{split}
    &\log(1+x) \\
    &\approx \frac{137x^5 + 33185x^4 + 931370x^3 - 13403630x^2 - 289469315x - 713567363}
    {30(x^5 + 505x^4 + 42010x^3 + 923010x^2 + 5722005x + 8040501)} \\
    &+ \log{20}
  \end{split}
\end{align}
Below is a graph of the absolute error of the scaled approximation and the exact value of $\log{(1+x)}$.
\begin{figure}[h]
    \centering
    \includegraphics[width=.9\linewidth]{figures/ModifiedQuadratureAbsoluteError.png}
    \caption{Graph of the absolute error of $\log{(1+x)}$ and the approximation in equation \ref{eq:scaledquadrature}}
    \label{fig:scaledquadrature}
\end{figure}

\subsection{Approximation for $x^\gamma$}
To approximate $x^\gamma$ for any $\gamma \in \mathbb{R}$, we rewrite $x^\gamma$ as follows:
\begin{align*}
  x^\gamma = e^{\log{x^\gamma}} = e^{\gamma\log{x}}.
\end{align*}
This expression can then be approximated using the Maclaurin series expansion for $e^x$, which converges for all $x$.
\begin{align*}
  e^x &= \sum_{n=0}^{\infty}{\frac{x^n}{n!}}\\
  \Rightarrow e^{\gamma\log{x}} &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align*}
As we already have an approximation for the natural logarithm, we can evaluate partial sums of the above infinite series to arrive at approximations for $x^\gamma$.
